Measuring cross correlation function line-profile variations in radial-velocity measurements via a Skew Normal distribution

### 2018-04-13 manuscript.tex
Add files via upload

>>>>

\subsection{Faculae} \label{sec:soap.faculae}

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 2.5in]{RV_comparison_FACULAE.pdf} 
\includegraphics[height = 2.5in]{SOAP_FACULAE_Comparison_para_SN.pdf} 
   \caption{SOAP FACULAE}
    \label{fig:faculae}
\end{figure*}

\subsection{Spot} \label{sec:soap.spot}

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 2.5in]{RV_comparison_SPOT.pdf} 
\includegraphics[height = 2.5in]{SOAP_SPOT_Comparison_para_SN.pdf} 
   \caption{SOAP SPOT}
    \label{fig:spot}
\end{figure*}

\subsection{Spot and planet} \label{sec:soap.spot.planet}

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 2.5in]{RV_comparison_PLANET_SPOT.pdf} 
\includegraphics[height = 2.5in]{SOAP_SPOT_PLANET_Comparison_para_SN.pdf} 
   \caption{SOAP PLANET and SPOT}
    \label{fig:spot.plus.planet}
\end{figure*}
